\begin{syllabus}

\course{CB101. Álgebra y Geometría}{Obligatorio}{CB101}

\begin{justification}
During the plenary sessions, lectures are held related to the design methodology.Also, during these sessions we will have presentations about entrepreneurship and startups related to engineering or technology.
During lab sessions, students form teams that maintain during the cycle. With the guidance of the teacher and through the methodology of Design Thinking developed in the plenary sessions, students should present innovative solutions to real problems inspired by the "Global Challenges" of the United Nations
The students will have a "Digital Log" that will be constantly reviewed by the teachers in charge. In it will be the advances, processes and referents of the group project. The course culminates with the presentations of the proposals put forward by the groups.


\end{justification}

\begin{goals}
\item Ability to design and carry out experiments.
\item Ability to analyze information.
\item Ability to design a system, component or process to meet the desired needs within realistic constraints (Level 1).
\item Capacity for teamwork.
\item Ability to lead a team
\item Oral communication skills (Level 1)
\item Written communication skills (Level 1)
\item Understands the impact of engineering solutions in a global, economic, environmental and society context.
\item Has interest in knowing about current issues of Peruvian society and the world
\end{goals}

\begin{outcomes}
\ExpandOutcome{a}{3}
\ExpandOutcome{i}{2}
\ExpandOutcome{j}{4}
\end{outcomes}

\begin{unit}{Sistemas de coordenadas. La recta.}{Lehmann05}{12}{4}
   \begin{topics}

      \item
      \item
      \item
   \end{topics}
   \begin{unitgoals}
      \item 
   \end{unitgoals}
\end{unit}

\begin{unit}{Cónicas y Coordenadas polares}{Lehmann05}{24}{3}
   \begin{topics}
      \item 
      \item 
   \end{topics}

   \begin{unitgoals}
      \item 
      \item
      \item 
      \end{unitgoals}
\end{unit}

\begin{unit}{Sistemas de ecuaciones. Matrices y determinantes}{Strang03,Grossman96}{24}{3}
   \begin{topics}
      \item 
      \item 
      \item 
      \end{topics}

   \begin{unitgoals}
      \item 
      \item 
      \item 
     
   \end{unitgoals}
\end{unit}

\begin{unit}{Vectores en $R^2$ y vectores en $R^3$}{Grossman96}{30}{3}
   \begin{topics}
      \item 
      \item 
   \end{topics}

   \begin{unitgoals}
      \item 
      \item 
      \item 
   \end{unitgoals}
\end{unit}



\begin{coursebibliography}
\bibfile{GeneralFormation/FG101D}
\end{coursebibliography}

\end{syllabus}
