\begin{syllabus}

\course{GH1102. Inglés II}{Obligatorio}{GH1102} % Common.pm

\begin{justification}
A fundamental part of the integral formation of a professional is the ability to communicate in a foreign language in addition to the native language itself. It not only broadens its cultural horizon but also allows a more humane and comprehensive view of people's lives. In the case of foreign languages, English is undoubtedly the most practical because it is spoken around the world. There is no country where it is not spoken.
In careers related to tourist services english is perhaps the most important practical tool that the student must master from the outset as part of his comprehensive education.
\end{justification}

\begin{goals}
\item Develop the ability to fluently speak the language..
\item Increase vocabulary and handle simple expressions
\end{goals}

\begin{outcomes}{V1}
\item \ShowOutcome{f}{2}
\end{outcomes}

\begin{competences}{V1}
    \item \ShowCompetence{C25}{f}
\end{competences}

\begin{unit}{How long ago?}{}{Soars021S,Cambridge06, MacGrew99}{0}{2}
   \begin{topics}
      \item Simple past
      \item Negative sentences with ago.
      \item Conjunctions
      \item Expressions of Time in past
      \item Phonetic relations and symbols
      \item Expressions to give the date
   \end{topics}

   \begin{learningoutcomes}
      \item At the end of the eighth unit, each student, understanding the grammar of the past tense is able to express a greater number of expressions of time and also to use prepositions to describe varied places and times. It is also capable of analyzing and expressing ideas about dates and numbers in order. 
   \end{learningoutcomes}

\end{unit}

\begin{unit}{Food you like!}{}{Soars021S, Cambridge06, MacGrew99}{0}{2}
   \begin{topics}
      \item Accounting and Non-Accounting Nouns
      \item Expressions with Would like and I'd like
      \item Quantifiers
      \item Meals around the world
      \item Formal requests
      \item Formal letters
   \end{topics}

   \begin{learningoutcomes}
      \item At the end of the ninth unit, students having identified how to express orders and make collections, uses in various situations. Express situations and states related to quantities. Explain and apply food and drinks vocabulary.
   \end{learningoutcomes}
\end{unit}

\begin{unit}{The world of work}{}{Soars021S, Cambridge06, MacGrew99}{0}{2}
   \begin{topics}
      \item Adjectives
      \item Sentences with Comparative Adjectives
      \item Sentences with Superlative Adjectives
      \item Cities and countryside
      \item Directional indications
   \end{topics}

   \begin{learningoutcomes}
      \item At the end of the tenth unit, students who have recognized the characteristics of adjectives use these to make comparisons of various types. Describes people and places and directions. They will use conjunctions to unite type ideas.
   \end{learningoutcomes}

\end{unit}

\begin{unit}{Looking good!}{}{Soars021S, Cambridge06, MacGrew99}{0}{2}
   \begin{topics}
      \item Present continuous
      \item Affirmative sentences, Negatives and Questions 
      \item Use of Whose
      \item Possessive pronouns
      \item Clothing and colors
      \item Expressions to wear in clothing stores
      \item Phonetic symbols.
   \end{topics}

   \begin{learningoutcomes}
      \item At the end of the eleventh unit, students having identified the idea of expressing ideas of actions that occur at the time or that relate at any time structure sentences in Present Progressive. They express ideas of possession with regard to clothes and colors.
   \end{learningoutcomes}

\end{unit}

\begin{unit}{Life is an adventure!}{}{Soars021S, Cambridge06, MacGrew99}{0}{2}
   \begin{topics}
      \item Use of going to
      \item Future time sentences
      \item Expressions of Quantity.
      \item Action verbs
      \item Vocabulary of the climate
      \item Expressions of Suggestion
      \item Write a postcard
   \end{topics}
   \begin{learningoutcomes}
      \item At the end of the twelfth unit, students, from the understanding of future time, will elaborate sentences using the necessary elements. They will also assimilate the need to express purposeful infinitives. They will acquire vocabulary to describe the climate. Expressions will be presented to make and ask for suggestions.
   \end{learningoutcomes}
\end{unit}

\begin{unit}{You`re pretty smart!}{}{Soars021S,Cambridge06,MacGrew99}{0}{2}
\begin{topics}
      \item Forms of Questions
      \item Adverbs and Adjectives
      \item Vocabulary description of feelings
      \item Expressions for train travel
      \item Writing Short Stories
      \item Readings
   \end{topics}

   \begin{learningoutcomes}
      \item At the end of the thirteenth unit, students having learned the fundamentals of structuring various questions, will perform application work in appropriate contexts. They emphasize the difference between adjectives and adverbs. They describe feelings. They use expressions to catch a train. They assume the idea is suffixes and prefixes.
   \end{learningoutcomes}

\end{unit}

\begin{unit}{Have you ever?}{}{Soars021S, Cambridge06, MacGrew99}{0}{2}
   \begin{topics}
      \item Perfect present
      \item Keywords with never, ever, and yet
      \item Vocabulary verbs in Past participle
      \item Expressions for airplane travel
      \item Writing thank-you letters
      \item Readings
   \end{topics}

   \begin{learningoutcomes}
      \item At the end of the fourteenth unit, students having known the fundamentals of the structure of the Present Perfect experience the need to express this type of time in actions. They will practice in appropriate contexts. They emphasize the difference between simple past and perfect present. Describe actions with never, ever, and yet. They use expressions to use at an airport.
   \end{learningoutcomes}

\end{unit}

\begin{coursebibliography}
\bibfile{ForeignLanguages/ID101}
\end{coursebibliography}

\end{syllabus}
%\end{document}
