\begin{syllabus}

\course{GH1002. Art and Technology }{Obligatorio}{GH1002}
% Source file: ../Curricula.in/lang/English/cycle/2020-I/Syllabi/GeneralEducation/GH1002.tex

\begin{justification}
The course seeks to give a global, historical and critical vision of the transformations and synergies of contemporary art. Where students approach two components of contemporary art and design: interdisciplinary practices and points of contact between the arts and the technological and engineering processes.
\end{justification}

\begin{goals}
    \item Develop the ability to analyze information.
    \item Develop the ability to interpret information.
    \item Develop the ability to work as a team.
    \item Developing Oral communication skills.
    \item Recognize the need for lifelong learning.   
\end{goals}

\begin{outcomes}{V1}
    \item \ShowOutcome{d}{2} % Multidiscip teams
    \item \ShowOutcome{e}{2} % ethical, legal, security and social implications
    \item \ShowOutcome{f}{2} % communicate effectively
    \item \ShowOutcome{n}{2} % Apply knowledge of the humanities
    \item \ShowOutcome{o}{2} % TASDSH
\end{outcomes}

\begin{competences}{V1}
    \item \ShowCompetence{C10}{d,n,o}
    \item \ShowCompetence{C17}{f}
    \item \ShowCompetence{C18}{f}
    \item \ShowCompetence{C21}{e}
\end{competences}

\begin{unit}{Arts and Technology.}{}{Wilson02}{12}{4}
   \begin{topics}
      \item What is art and what is it for?
      \item The artistic discourse: identity, territory, politics and society.
   \end{topics}
   \begin{learningoutcomes}
      \item Promote the  interest in learn about current issues of Peruvian society and the world.
   \end{learningoutcomes}
\end{unit}

\begin{unit}{Digital Art}{}{Maeda12}{24}{3}
   \begin{topics}
      \item Generative Art.
      \item Net Art.
      \item Virtual Reality.
   \end{topics}

   \begin{learningoutcomes}
      \item Development of skills such as: creativity, critical thinking, observation and synthesis.
      \end{learningoutcomes}
\end{unit}

\begin{unit}{Prototyping, analysis and creation}{}{Wilson02}{24}{3}
   \begin{topics}
      \item Digital Manufacturing
      \item Intervention: Action and public space
      \item Presentation: Montage and portafolio
      \end{topics}

   \begin{learningoutcomes}
      \item Students understand the importance and effectiveness of teamwork, in both academic and professional life. During the semester, students perform group and individual activities whose common goal is the generation of a project that links concepts of art,
           technology and engineering.
     
   \end{learningoutcomes}
\end{unit}

\begin{coursebibliography}
\bibfile{GeneralEducation/GH1002}
\end{coursebibliography}
\end{syllabus}
