\begin{syllabus}

\course{GH0016. Leadership and Negotiation }{Obligatorio}{GH0016}
% Source file: ../Curricula.in/lang/English/cycle/2020-I/Syllabi/GeneralEducation/GH2016.tex

\begin{justification}
This course is designed to help students to develop skills related to leadership, as well as to introduce them to the essential elements of a negotiation, in order for them to gain experience and confidence to function well in their work environments. The aim of the
course is to train students in the necessary tools to become integer and resolute professionals that are capable of facing individual and collective challenges. Learning takes place through experience and critical thinking. To do this, students will be exposed
to different subjects and activities the allow different ways of thinking and decision making. Always on the basis of three axes: ethical rules, constant self-evaluation and the planning of activities.
\end{justification}

\begin{goals}
\item Ability to analyze information.
\item Ability to identify problems.
\item Ability to formulate solution alternatives.
\item Understand professional responsibilities and ethics.
\item Ability to lead a team.
\end{goals}

\begin{outcomes}{V1}
    \item \ShowOutcome{d}{2} % Multidiscip teams
    \item \ShowOutcome{e}{2} % ethical, legal, security and social implications
    \item \ShowOutcome{f}{2} % communicate effectively
    \item \ShowOutcome{n}{2} % Apply knowledge of the humanities
    \item \ShowOutcome{o}{2} % TASDSH
\end{outcomes}

\begin{competences}{V1}
    \item \ShowCompetence{C10}{d,n,o}
    \item \ShowCompetence{C17}{f}
    \item \ShowCompetence{C18}{f}
    \item \ShowCompetence{C21}{e}
\end{competences}

\begin{unit}{Leadership and Negotiation}{}{Caravedo11,Robbins04}{12}{4}
   \begin{topics}
      \item Introduction to Leadership and Negotiation.
      \item Self-assessment of Leadership.
      \item Leadership: Influence and motivation .  
      \item Competency interview.
      \item Leading communication.   
      \item Experiential application of leading competencies.
      \item Leadership and negotiation.
      \item Bipartisan negotiation.
      \item Negotiation and teamwork .
      \item Benefit negotiation.
      \item Negotiation and ethics .  
 
      
   \end{topics}
   \begin{learningoutcomes}
      \item Development of leadership potential through case studies, dynamics and assessment center in classes with specialized coaches.
   \end{learningoutcomes}
\end{unit}

\begin{coursebibliography}
\bibfile{GeneralEducation/GH2016}
\end{coursebibliography}

\end{syllabus}
