\newcommand{\ContribInitMsg}{This discipline contributes to the achievement of the following outcomes\xspace}
\newcommand{\CompetencesInitMsg}{This discipline contributes to the the following competences in the area of computing (IEEE)\xspace}

\DefineOutcome{a}{An ability to apply knowledge of mathematics, science.\xspace}
\DefineOutcome{aShort}{Apply computer and math skills.\xspace}
\DefineSpecificOutcome{a}{1}{a1}{Apply demonstration techniques (direct method, contrapositive, induction and contradiction) to demonstrate properties in discrete structures and algorithms.\xspace}
\DefineSpecificOutcome{a}{2}{a2}{Use logical propositions in an orderly manner.\xspace}
\DefineSpecificOutcome{a}{3}{a3}{Apply counting techniques in solving computer problems.\xspace}
\DefineSpecificOutcome{a}{4}{a4}{Apply efficient techniques for solving computer problems.\xspace}
\DefineSpecificOutcome{a}{5}{a5}{Apply efficient techniques to solve computer problems in parallel and distributed environments.\xspace}
\DefineSpecificOutcome{a}{6}{a6}{Analyze and compare sequential and parallel applications.\xspace}
\DefineSpecificOutcome{a}{7}{a7}{Transform, when the situation requires it, sequential to parallel applications efficiently.\xspace}

\DefineSpecificOutcome{a}{8}{a8}{Apply finite-state machine and automaton techniques in the resolution of computer problems.\xspace}
\DefineSpecificOutcome{a}{9}{a9}{Apply techniques and knowledge of computer architecture for the generation and optimization of code.\xspace}
\DefineSpecificOutcome{a}{10}{a10}{Make a computational analysis that allows calculating the execution time of a given algorithm.\xspace}
\DefineSpecificOutcome{a}{11}{a11}{Use mathematical techniques that allow to delimit sums and to solve recurrences that reflect the computational costs of an algorithm.\xspace}
\DefineSpecificOutcome{a}{12}{a12}{Evaluate and apply computational thinking to solve everyday problems\xspace}
\DefineSpecificOutcome{a}{13}{a13}{Efficiently use conditional, repetitive control structures, functions, recursion, sorting and search.\xspace}
\DefineSpecificOutcome{a}{14}{a14}{Properly use files for storage and retrieval of information.\xspace}
\DefineSpecificOutcome{a}{15}{a15}{Use count theory definitions to solve sorting or selection problems in a set of single and repeated elements.\xspace}
\DefineSpecificOutcome{a}{16}{a16}{Solve counting problems using generator functions.\xspace}
\DefineSpecificOutcome{a}{17}{a17}{Define functions by recognizing dependent and independent variables by recognizing functions as parameters\xspace}
\DefineSpecificOutcome{a}{18}{a18}{Build and model functions from a given context.\xspace}
\DefineSpecificOutcome{a}{19}{a19}{Recognize the behavior of functions through rates of variation.\xspace}
\DefineSpecificOutcome{a}{20}{a20}{Analyze the extreme values of a function.\xspace}
\DefineSpecificOutcome{a}{21}{a21}{Recognize the use of integrals defined as differential accumulation.\xspace}
% New here Grace
\DefineSpecificOutcome{a}{22}{a22}{Apply operations on matrices to build algorithms.\xspace}
\DefineSpecificOutcome{a}{23}{a23}{Apply probability theory and Bayes' theorem to the construction of probability network models(\textit{Probabilistic graphical models}).\xspace}
\DefineSpecificOutcome{a}{24}{a24}{Apply sampling and cross validation techniques\xspace}
\DefineSpecificOutcome{a}{25}{a25}{Apply informed and uninformed search computer techniques.\xspace}
\DefineSpecificOutcome{a}{26}{a26}{Apply computer vision techniques.\xspace}
\DefineSpecificOutcome{a}{27}{a27}{Apply natural language processing techniques.\xspace}
\DefineSpecificOutcome{a}{28}{a28}{Apply machine learning techniques.\xspace}
\DefineSpecificOutcome{a}{29}{a29}{Demonstrate math and computer skills in an integrated final project\xspace}
\DefineSpecificOutcome{a}{30}{a30}{Apply basic concepts of set theory, relationships and functions.\xspace}
\DefineSpecificOutcome{a}{31}{a31}{Apply the computational concept of non-determinism in problem solving.\xspace}
\DefineSpecificOutcome{a}{32}{a32}{Apply linear transformation to solve problems in computer graphics, artificial intelligence, information management, and simulation.\xspace}
\DefineSpecificOutcome{a}{33}{a33}{Analyze and apply the computational cost in a metric space.\xspace}
\DefineSpecificOutcome{a}{34}{a34}{Analyze and apply multimensional access methods in georeferenced query problems.\xspace}
\DefineSpecificOutcome{a}{35}{a35}{Analyze and apply multi-mensional access methods with temporal variation.\xspace}
\DefineSpecificOutcome{a}{36}{a36}{Analyze the problem of high dimensions in the efficiency of a query.\xspace}
\DefineSpecificOutcome{a}{37}{a37}{Calculate position (mean, median, mode) and dispersion (standard deviation, range, interquartile range) descriptors of observations of a random variable.\xspace}
\DefineSpecificOutcome{a}{38}{a38}{Use position (mean, median, mode) and dispersion (standard deviation, range, interquartile range) descriptors to make decisions on real problems such as determining the average gain or warranty period of a product.\xspace}
\DefineSpecificOutcome{a}{39}{a39}{Visualize (histograms, boxplot and scatter plot) a set of observations of a random variable to understand its behavior\xspace}

%Apply knowledge of GPU programming
\DefineSpecificOutcome{a}{40}{a40}{Apply GPU programming knowledge.\xspace}
\DefineSpecificOutcome{a}{41}{a41}{Implement tensioners on GPUs.\xspace}
\DefineSpecificOutcome{a}{42}{a42}{Demonstrate mastery and application of neural network models to real-world problems\xspace}
\DefineSpecificOutcome{a}{43}{a43}{Demonstrate mastery and application of evolutionary algorithms to real-world problems\xspace}
\DefineSpecificOutcome{a}{44}{a44}{Demonstrate mastery and application of fuzzy logic in real problems\xspace}
%Apply knowledge of a modern 3D graphics library via practical assignments
\DefineSpecificOutcome{a}{45}{a45}{Apply modern libraries for 3D graphics.\xspace}
%Ability to produce usable graphics user-interfaces
\DefineSpecificOutcome{a}{46}{a46}{Produce useful graphical user interfaces.\xspace}
%Ability to manipulate 3D objects in virtual environments
\DefineSpecificOutcome{a}{47}{a47}{Manipulate 3D objects in virtual environments\xspace}
\DefineSpecificOutcome{a}{48}{a48}{Apply data visualization and/or computer vision and/or GPU programming and/or augmented reality and/or virtual reality to solve problems in our environment.\xspace}
\DefineSpecificOutcome{a}{49}{a49}{Apply mathematical methods and concepts in an encryption process to protect information\xspace}
\DefineSpecificOutcome{a}{50}{a50}{Apply mathematics in different types of encryption: symmetric, asymmetric and hashing.\xspace}
\DefineSpecificOutcome{a}{51}{a51}{Apply mathematics in robotics projects.\xspace}
\DefineSpecificOutcome{a}{52}{a52}{Apply linear algebra to understand and implement \textit{deep learning} algorithms\xspace} 
\DefineSpecificOutcome{a}{53}{a53}{Calculate and apply the process of falling objects considering different forces of opposition to the movement.\xspace}
\DefineSpecificOutcome{a}{54}{a54}{Use the relationship between speed, frequency and wavelength for a periodic wave.\xspace}
\DefineSpecificOutcome{a}{55}{a55}{Interpret and use the mathematical expression for a sine-periodic wave\xspace}
\DefineSpecificOutcome{a}{56}{a56}{Calculate the speed of waves in a string.\xspace}
\DefineSpecificOutcome{a}{57}{a57}{Describe the rotation of a rigid body in terms of angular coordinate, angular velocity and angular acceleration.\xspace}
\DefineSpecificOutcome{a}{58}{a58}{Apply data structures and algorithms to address biological problems from a computational perspective.\xspace}

\DefineOutcome{b}{An ability to design and conduct experiments, as well as to analyze and interpret data.\xspace}
\DefineOutcome{bShort}{Analyze problems and identify and define computational requirements.\xspace}
\DefineSpecificOutcome{b}{1}{b1}{Apply computational thinking effectively to the solution of everyday problems\xspace}
\DefineSpecificOutcome{b}{2}{b2}{Evaluate different proposals for computational thinking for the same problem.\xspace}
\DefineSpecificOutcome{b}{3}{b3}{Apply robotics as a means to develop computational thinking.\xspace}
\DefineSpecificOutcome{b}{4}{b4}{Identify and efficiently apply various algorithmic strategies and data structures for the solution of a problem given certain space and time constraints.\xspace}
\DefineSpecificOutcome{b}{5}{b5}{Identify and efficiently apply diverse algorithmic strategies and data structures for the solution of a problem in parallel and distributed environments.\xspace}
\DefineSpecificOutcome{b}{6}{b6}{Implement distributed solutions using MapReduce.\xspace}
\DefineSpecificOutcome{b}{7}{b7}{Implement distributed solutions using NoSql databases.\xspace}
\DefineSpecificOutcome{b}{8}{b8}{Apply machine learning techniques to large data sets.\xspace}
\DefineSpecificOutcome{b}{9}{b9}{Apply machine learning techniques for the processing and analysis of large volumes obtained in real time\xspace}

\DefineSpecificOutcome{b}{10}{b10}{Implement distributed solutions using network databases.\xspace}
\DefineSpecificOutcome{b}{11}{b11}{Understand the difference between an NP-difficult problem and one that has a polynomial solution.\xspace}
\DefineSpecificOutcome{b}{12}{b12}{Given a problem with a polynomial solution, identify whether it can be solved by a voracious strategy, by a dynamic scheduling strategy or by a strategy of divide and conquer taking into account the size of the input.\xspace}
\DefineSpecificOutcome{b}{13}{b13}{Modeling database through ER, MR, optimization, transaction and information retrieval models\xspace}
\DefineSpecificOutcome{b}{14}{b14}{Design the appropriate hardware resources for computing.\xspace}
\DefineSpecificOutcome{b}{15}{b15}{Learn and apply techniques and mechanisms to perform efficient computing on hardware.\xspace}
\DefineSpecificOutcome{b}{16}{b16}{Understand the implementation of an Operating System to make efficient use of the hardware available in a system.\xspace}
\DefineSpecificOutcome{b}{17}{b17}{Study and apply various techniques of efficient control of resources to achieve the processing of information.\xspace}
\DefineSpecificOutcome{b}{18}{b18}{Define requirements in an integrated fine project.\xspace}
\DefineSpecificOutcome{b}{19}{b19}{Understand the difference between a problem without a solution (undecidable problem) and a problem that does have a solution\xspace}
\DefineSpecificOutcome{b}{20}{b20}{Identify and solve a problem that is solvable by automata theory and recognize which is the simplest type of automata that solves the problem.\xspace}
\DefineSpecificOutcome{b}{21}{b21}{Make the budget required to execute a software-based solution.\xspace}
\DefineSpecificOutcome{b}{22}{b22}{Write programs from a practical specification and produce realistic graphics.\xspace}
\DefineSpecificOutcome{b}{23}{b23}{Write programs oriented to solve problems in our environment using computer graphics.\xspace}
\DefineSpecificOutcome{b}{24}{b24}{Analyze the computational power needed to be able to decipher and calculate the value of a key.\xspace}
\DefineSpecificOutcome{b}{25}{b25}{Analyze and understand the context of a problem to solve it through robotics.\xspace}

\DefineSpecificOutcome{b}{26}{b26}{Describe the rotation of a rigid body in terms of angular coordinate, angular speed and angular acceleration.\xspace}
\DefineSpecificOutcome{b}{27}{b27}{Analyze the rotation of a rigid body when the angular acceleration is constant.\xspace}
\DefineSpecificOutcome{b}{28}{b28}{Relate the rotation of a rigid body to the linear velocity and acceleration of a point on the body.\xspace}
\DefineSpecificOutcome{b}{29}{b29}{The meaning of the body's moment of inertia around an axis and how it relates to rotational kinetic energy.\xspace}

\DefineOutcome{c}{An ability to design a system, component, or process to meet desired needs within realistic constraints such as economic, environmental, social, political, ethical, health and safety, manufacturability, and sustainability.\xspace}
\DefineOutcome{cShort}{Design, implement and evaluate a computer system, process, component or program.\xspace}
\DefineSpecificOutcome{c}{1}{c1}{Identify and implement data structures for the solution of a computer problem\xspace}
\DefineSpecificOutcome{c}{2}{c2}{Design and develop information systems that implement business rules.\xspace}
\DefineSpecificOutcome{c}{3}{c3}{Use different tools and programming languages in the software components (\textit{Full stack}).\xspace}
\DefineSpecificOutcome{c}{4}{c4}{Design and implement scalable software architectures in different platforms.\xspace}
\DefineSpecificOutcome{c}{5}{c5}{Describe how platform-based development differs from the general purpose of programming.\xspace}
\DefineSpecificOutcome{c}{6}{c6}{Apply the advantages and disadvantages of cross-platform constraints.\xspace}
\DefineSpecificOutcome{c}{7}{c7}{Apply or implement Web platform constraints in software development\xspace}
\DefineSpecificOutcome{c}{8}{c8}{Apply web standards.\xspace}
\DefineSpecificOutcome{c}{9}{c9}{Apply development standards for mobile devices\xspace}
\DefineSpecificOutcome{c}{10}{c10}{Implement software as a service.\xspace}
\DefineSpecificOutcome{c}{11}{c11}{Design and implement integrated software.\xspace}
\DefineSpecificOutcome{c}{12}{c12}{Understand how the layers of the TCP/IP model work.\xspace}
\DefineSpecificOutcome{c}{13}{c13}{Define and implement components of a network system to provide better service on the Internet.\xspace}
\DefineSpecificOutcome{c}{14}{c14}{Evaluate the performance of innovative technologies for Internet operation.\xspace}
\DefineSpecificOutcome{c}{15}{c15}{Integrate various networking technologies to improve the quality of service to the end user.\xspace}
\DefineSpecificOutcome{c}{16}{c16}{Implement a spatial or metric data structure in an open database engine.\xspace}
\DefineSpecificOutcome{c}{17}{c17}{Apply human factors and colors to create user-friendly interfaces.\xspace}
\DefineSpecificOutcome{c}{18}{c18}{Evaluate interfaces in an objective way using already validated heuristics and methodologies.\xspace}
\DefineSpecificOutcome{c}{19}{c19}{Evaluate the efficiency of an interface in terms of usability.\xspace}
\DefineSpecificOutcome{c}{20}{c20}{Evaluate the efficiency of an interface in terms of resource consumption.\xspace}
\DefineSpecificOutcome{c}{21}{c21}{Calculate the time of and information transmission.\xspace}
\DefineSpecificOutcome{c}{22}{c22}{Design a robotic-based solution to a specific problem.\xspace}

\DefineOutcome{d}{An ability to function on multidisciplinary teams.\xspace}
\DefineOutcome{dShort}{Work effectively on teams.\xspace}
\DefineSpecificOutcome{d}{1}{d1}{Collaborative software development using code repositories and version management (e.g., Git, Bitbucket, SVN)\xspace}
\DefineSpecificOutcome{d}{2}{d2}{Developing group presentations and reports on specific topics.\xspace}
\DefineSpecificOutcome{d}{3}{d3}{Develop group work on each course topic.\xspace}
\DefineSpecificOutcome{d}{4}{d4}{Collaboratively develop business plans for technology companies.\xspace}
\DefineSpecificOutcome{d}{5}{d5}{Develop software that is ready to be integrated with other components or pieces of software\xspace}
\DefineSpecificOutcome{d}{6}{d6}{Develop skills to improve interpersonal relationships by valuing the participation of all team members.\xspace}
\DefineSpecificOutcome{d}{7}{d7}{Develop skills to lead a team such as: inspiration, motivation, planning, delegation and feedback.\xspace}
\DefineSpecificOutcome{d}{8}{d8}{Develop skills to know how to align personal objectives with institutional ones.\xspace}
\DefineSpecificOutcome{d}{9}{d9}{Analyze the strengths and weaknesses of a team to build an efficient and ethical solution to a problem.\xspace}
\DefineSpecificOutcome{d}{10}{d10}{Develop skills to generate confidence in the work team and in the social environment.\xspace}

\DefineOutcome{e}{Understand correctly the professional, ethical, legal, security and social implications of the profession.\xspace}
\DefineOutcome{eShort}{Understand the professional, ethical, legal, security and social implications.\xspace}
\DefineSpecificOutcome{e}{1}{e1}{Demonstrate a proper understanding of the ethical implications of the software you build.\xspace}
\DefineSpecificOutcome{e}{2}{e2}{Demonstrate a proper understanding of the safety implications of the software you build.\xspace}
\DefineSpecificOutcome{e}{3}{e3}{Determine the value of the information to prioritize the level of protection required\xspace}
\DefineSpecificOutcome{e}{4}{e4}{Identify the risks that may be involved in the operation of computer equipment within a given context\xspace}
\DefineSpecificOutcome{e}{5}{e5}{Understand, apply and manage protection and security systems in their different states and formats.\xspace}
\DefineSpecificOutcome{e}{6}{e6}{Develop software that guarantees the privacy of potential users' data.\xspace}
\DefineSpecificOutcome{e}{7}{e7}{Analyze, from an ethical perspective, the professional, legal, security and social implications involved in software development.\xspace}
\DefineSpecificOutcome{e}{8}{e8}{Develop the ability to read ethics from the perspective of the human virtues (prudence, temperance, strength and justice) of professional and social reality\xspace}
\DefineSpecificOutcome{e}{9}{e9}{Promote an ethic that founds the professional skills that are formed during the career.\xspace}

\DefineOutcome{f}{An ability to communicate effectively.\xspace}
\DefineOutcome{fShort}{Communicate effectively.\xspace}
\DefineSpecificOutcome{f}{1}{f1}{Clearly transmit technical proposals to audiences in other areas.\xspace}
\DefineSpecificOutcome{f}{2}{f2}{Transmit technical proposals in the area of computing in English.\xspace}
\DefineSpecificOutcome{f}{3}{f3}{Transmit technical proposals in English to audiences in other areas.\xspace}
\DefineSpecificOutcome{f}{4}{f4}{Present a business plan to potential investors.\xspace}

\DefineSpecificOutcome{f}{5}{f5}{Listening. Can follow a very slow and carefully articulated speech to assimilate meaning.\xspace}
\DefineSpecificOutcome{f}{6}{f6}{Speaking. Can produce simple mainly isolated phrases about people and places.\xspace}
\DefineSpecificOutcome{f}{7}{f7}{Reading. Can understand very short, simple texts a single phrase at a time, picking up familiar names, words and basic phrases.\xspace}
\DefineSpecificOutcome{f}{8}{f8}{Writing. Can write simple isolated phrases and sentences.\xspace}

\DefineSpecificOutcome{f}{9}{f9}{Listening. Can understand a clearly and slowly articulated speech related to areas of most immediate priority.\xspace}
\DefineSpecificOutcome{f}{10}{f10}{Speaking. Can give a simple description or presentation as a short series of simple phrases and sentences linked into a list.\xspace}
\DefineSpecificOutcome{f}{11}{f11}{Reading. Can understand short, simple texts containing the highest frequency vocabulary.\xspace}
\DefineSpecificOutcome{f}{12}{f12}{Writing. Can write a series of simple phrases and sentences linked with simple connectors.\xspace}
\DefineSpecificOutcome{f}{13}{f13}{Listening. Can understand enough to be able to meet needs of a concrete type.\xspace}
\DefineSpecificOutcome{f}{14}{f14}{Reading. Can understand short, simple texts on familiar matters of a concrete type which consist of high frequency every day or job-related language.\xspace}

\DefineSpecificOutcome{f}{15}{f15}{Listening. Can understand the main points of clear standard speech on familiar matters, including short narratives.\xspace}
\DefineSpecificOutcome{f}{16}{f16}{Speaking. Can reasonably fluently sustain a straightforward description of one of a variety of subjects within his/her field of interest.\xspace}
\DefineSpecificOutcome{f}{17}{f17}{Reading. Can read straightforward factual texts on subjects related to his/her field and interest with a satisfactory level of comprehension.\xspace}
\DefineSpecificOutcome{f}{18}{f18}{Writing. Can write straightforward connected texts on a range of familiar subjects by linking a series of shorter discrete elements into a linear sequence.\xspace}
\DefineSpecificOutcome{f}{19}{f19}{Listening. Can understand straightforward factual information in a generally familiar accent.\xspace}
\DefineSpecificOutcome{f}{20}{f20}{Speaking. Can reasonably fluently sustain a straightforward description of one of a variety of subjects within his/her field of interest, presenting it as a linear sequence of points.\xspace}

\DefineSpecificOutcome{f}{21}{f21}{Management of intellectual skills such as memory, concentration, mental agility and creativity.\xspace}
\DefineSpecificOutcome{f}{22}{f22}{Management of voice, body and facial expression.\xspace}
\DefineSpecificOutcome{f}{23}{f23}{Strengthen self-esteem, security and overcome shyness (not understood as introversion).\xspace}
\DefineSpecificOutcome{f}{24}{f24}{Develop clarity, accuracy, linguistic correctness, conciseness and elegance when speaking in a speech.\xspace}
\DefineSpecificOutcome{f}{25}{f25}{Develop voice qualities such as: volume, speed, tone, flexibility and intonation through breathing exercises.\xspace}
\DefineSpecificOutcome{f}{26}{f26}{Develop knetic and proxemic skills such as: gestures, use of the hands (mimics and gestures), look, body postures and movements.\xspace}
\DefineSpecificOutcome{f}{27}{f27}{Structure discourses for different areas such as: scientific, academic and social.\xspace}
\DefineSpecificOutcome{f}{28}{f28}{Apply team leadership tools such as: effective communication, emotional intelligence, time management, decision making, creativity and innovation, mentoring.\xspace}

\DefineOutcome{g}{The broad education necessary to understand the impact of computing solutions in a global, economic, environmental, and societal context.\xspace}
\DefineOutcome{gShort}{Analyze the local and global impact of computing.\xspace}
\DefineSpecificOutcome{g}{1}{g1}{Develop solutions that solve an existing problem in our society.\xspace}
\DefineSpecificOutcome{g}{2}{g2}{Design efficient software solutions based on a correct understanding of the architecture of a computer or a group of them.\xspace}
\DefineSpecificOutcome{g}{3}{g3}{Analyze the impact of a computer solution on individuals.\xspace}
\DefineSpecificOutcome{g}{4}{g4}{Analyze the impact of a computer solution on organizations.\xspace}
\DefineSpecificOutcome{g}{5}{g5}{Analyze the impact of a computer solution on society.\xspace}
\DefineSpecificOutcome{g}{6}{g6}{Analyze the local impact of a solution.\xspace}
\DefineSpecificOutcome{g}{7}{g7}{Analyze the global impact of a solution.\xspace}
\DefineSpecificOutcome{g}{8}{g8}{Analyze the impact of potential security threats on individuals, organizations and society.\xspace}
\DefineSpecificOutcome{g}{9}{g9}{Analyze the impact of automation produced by robotics on the creation and transformation of existing jobs.\xspace}
\DefineSpecificOutcome{g}{10}{g10}{Analyze the impact of cloud computing on organizations\xspace}

\DefineOutcome{h}{A recognition of the need for, and an ability to engage in life-long learning.\xspace}
\DefineOutcome{hShort}{Lifelong learning.\xspace}
\DefineSpecificOutcome{h}{1}{h1}{Develop research projects with levels of complexity appropriate for undergraduate study.\xspace}
\DefineSpecificOutcome{h}{2}{h2}{Demonstrate the ability to learn to learn autonomously.\xspace}
\DefineSpecificOutcome{h}{3}{h3}{Use data collected from computer events to prevent future attacks\xspace}
\DefineSpecificOutcome{h}{4}{h4}{Learn how to make a good source of information.\xspace}
\DefineSpecificOutcome{h}{5}{h5}{Learn to do a correct reading of a scientific paper in the area.\xspace}

\DefineOutcome{i}{An ability to use the techniques, skills, and modern computing tools necessary for computing practice.\xspace}
\DefineOutcome{iShort}{Use current techniques and tools.\xspace}
\DefineSpecificOutcome{i}{1}{i1}{Develop components using modern computer techniques that implement functionality and are useful for various information systems.\xspace}
\DefineSpecificOutcome{i}{2}{i2}{Use programming languages and environments that allow the implementation and debugging of solutions.\xspace}
\DefineSpecificOutcome{i}{3}{i3}{Properly use the query optimization, performance, indexing and table fragmentation modules for distributed DBs using an open source database engine such as PostgreSQL, Cassandra or MongoDB\xspace}
\DefineSpecificOutcome{i}{4}{i4}{Use software verification and validation techniques.\xspace}
\DefineSpecificOutcome{i}{5}{i5}{Use continuous integration techniques and tools.\xspace}
\DefineSpecificOutcome{i}{6}{i6}{Understand and study instruction-level parallelism in a processing element.\xspace}
\DefineSpecificOutcome{i}{7}{i7}{Analyze the results of network traffic measurements using \textit{Open Source} tools.\xspace}
\DefineSpecificOutcome{i}{8}{i8}{Integrate network technologies for better Internet service.\xspace}
\DefineSpecificOutcome{i}{9}{i9}{Use GPUs as a very important tool for creating computer graphics.\xspace}
\DefineSpecificOutcome{i}{10}{i10}{Use modern techniques and tools for the detection and reduction of risks due to possible vulnerabilities.\xspace}
\DefineSpecificOutcome{i}{11}{i11}{Use and manage microservice containers to create scalable applications\xspace}
\DefineSpecificOutcome{i}{12}{i12}{Know the importance of the net force on an object and what happens when the net force is zero.\xspace}
\DefineSpecificOutcome{i}{13}{i13}{Know the relationship between the net force on an object, the object's mass and its acceleration.\xspace}
\DefineSpecificOutcome{i}{14}{i14}{Know how the forces that two objects exert on each other are related.\xspace}
\DefineSpecificOutcome{i}{15}{i15}{Apply dynamic programming, cluster detection methods (\textit{clustering}) and heuristics to solve biological problems\xspace}
\DefineSpecificOutcome{i}{16}{i16}{Learn to use tools for writing scientific documents/articles.\xspace}
\DefineSpecificOutcome{i}{17}{i17}{Apply sensor network concepts to the development of IoT solutions.\xspace}

\DefineOutcome{j}{Apply the mathematical basis, principles of algorithms and the theory of Computer Science in the modeling and design of computational systems in such a way as to demonstrate understanding of the equilibrium points involved in the chosen option.\xspace}
\DefineOutcome{jShort}{Apply mathematics, algorithms and CS theory in system modeling and design.\xspace}
\DefineSpecificOutcome{j}{1}{j1}{Solve recurrence problems to simplify algorithmic complexity\xspace}
\DefineSpecificOutcome{j}{2}{j2}{Apply graph and tree theory for optimization and problem solving\xspace}
\DefineSpecificOutcome{j}{3}{j3}{Properly use tools such as RelaX \textit{Relational Algebra Calculator} (https://dbis-uibk.github.io/relax/calc.htm) to verify the relational algebra of a query.\xspace}
\DefineSpecificOutcome{j}{4}{j4}{Solve contextualized problems in the area of computing by applying differential and integral calculus techniques.\xspace}
\DefineSpecificOutcome{j}{5}{j5}{Propose basic models based on a science context using differential equations.\xspace}
\DefineSpecificOutcome{j}{6}{j6}{Solve differential equations that model problems in different science contexts using different integration techniques.\xspace}
\DefineSpecificOutcome{j}{7}{j7}{Apply automaton theory for optimization and problem solving.\xspace}
\DefineSpecificOutcome{j}{8}{j8}{Apply linear transformations and algorithms to solve computational problems\xspace}
\DefineSpecificOutcome{j}{9}{j9}{Use linear algebra to determine the coefficients in a multiple regression model to explain a random variable as a function of others\xspace}
\DefineSpecificOutcome{j}{10}{j10}{Perform residue analysis of a regression to validate a regression model and establish the statistical significance of its coefficients.\xspace}
\DefineSpecificOutcome{j}{11}{j11}{Apply lighting concepts and text rendering to create realistic 3D graphics.\xspace}
\DefineSpecificOutcome{j}{12}{j12}{Apply GPU programming to understand how modern graphics computing works\xspace}
\DefineSpecificOutcome{j}{13}{j13}{Write a sound wave in terms of particle displacements or pressure fluctuations\xspace}
\DefineSpecificOutcome{j}{14}{j14}{Calculate the speed of sound waves in different materials.\xspace}
\DefineSpecificOutcome{j}{15}{j15}{Obtain the intensity of a sound wave.\xspace}
\DefineSpecificOutcome{j}{16}{j16}{Know what determines the specific frequency of the sound produced by an organ or a flute\xspace}
\DefineSpecificOutcome{j}{17}{j17}{Know how resonance occurs in musical instruments.\xspace}

\DefineOutcome{k}{Apply the principles of development and design in the construction of software systems of variable complexity.\xspace}
\DefineOutcome{kShort}{Apply principles of development and design in software of variable complexity.\xspace}
\DefineSpecificOutcome{k}{1}{k1}{Perform adequately as part of an information system implementation project.\xspace}
\DefineSpecificOutcome{k}{2}{k2}{Perform adequately as part of a software implementation project\xspace}
\DefineSpecificOutcome{k}{3}{k3}{Apply software development methodologies.\xspace}
\DefineSpecificOutcome{k}{4}{k4}{Use programming paradigms to build software.\xspace}
\DefineSpecificOutcome{k}{5}{k5}{Use algorithm techniques and data structures to build scalable software.\xspace}
\DefineSpecificOutcome{k}{6}{k6}{Use the principles of software architecture to build reliable software products.\xspace}
\DefineSpecificOutcome{k}{7}{k7}{Measure quality attributes of software components.\xspace}
\DefineSpecificOutcome{k}{8}{k8}{Design and build software components that integrate with other existing ones (\textit{Legacy}).\xspace}
\DefineSpecificOutcome{k}{9}{k9}{Plan and manage software development projects.\xspace}
\DefineSpecificOutcome{k}{10}{k10}{Demonstrate mastery of the principles of quality software development in an integrated project\xspace}

% Our outcomes are here !
\DefineOutcome{l}{Develop principles research in the area of computing with levels of international competitiveness.\xspace}
\DefineOutcome{lShort}{Develop principles of research with international level.\xspace}
\DefineSpecificOutcome{l}{1}{l1}{Demonstrate that you have developed research according to an undergraduate level.\xspace}
\DefineSpecificOutcome{l}{2}{l2}{Solve problems in our environment based on new proposals for solutions based on computer graphics.\xspace}
\DefineSpecificOutcome{l}{3}{l3}{Solve problems of our environment based on new proposals of solutions based on software development.\xspace}
\DefineSpecificOutcome{l}{4}{l4}{Investigate new solutions to existing problems based on robotics\xspace}
\DefineSpecificOutcome{l}{5}{l5}{Investigate at a formative level new solutions to existing problems based on artificial intelligence.\xspace}
\DefineSpecificOutcome{l}{6}{l6}{Learn howw to choose a research topic.\xspace}
\DefineSpecificOutcome{l}{7}{l7}{Learn how to organize relevant information related to a research topic.\xspace}
\DefineSpecificOutcome{l}{8}{l8}{Learn to critique a scientific article.\xspace}
\DefineSpecificOutcome{l}{9}{l9}{Write a scientific article consistently.\xspace}
\DefineSpecificOutcome{l}{10}{l10}{Learn to choose the means to publish research.\xspace}

\DefineOutcome{m}{Transform your knowledge of the area of Computer Science into technological enterprises.\xspace}
\DefineOutcome{mShort}{Transform your knowledge into technological ventures.\xspace}
\DefineSpecificOutcome{m}{1}{m1}{Create a technology-based company in the country and / or internationally.\xspace}

\DefineOutcome{n}{Apply knowledge of the humanities in their professional work.\xspace}
\DefineOutcome{nShort}{Apply knowledge of the humanities in their professional work.\xspace}
\DefineOutcome{HUShort}{Apply knowledge of the humanities in their professional work.\xspace}
\DefineSpecificOutcome{n}{1}{n1}{Complement their professional work through a better understanding of other disciplines.\xspace}
\DefineSpecificOutcome{n}{2}{n2}{Apply interpersonal tools in the profession such as: body and verbal expression, interaction, empathy, tolerance, patience.\xspace}
\DefineSpecificOutcome{n}{3}{n3}{Apply in the profession intra personal skills such as: memory, concentration, mental agility and creativity.\xspace}
\DefineSpecificOutcome{n}{4}{n4}{Strengthen professional development through good self-esteem and overcoming shyness.\xspace}
%OnlyUCSP
\DefineOutcome{ñ}{Understand that the formation of a good professional is not disconnected or opposed but rather contributes to genuine personal growth. This requires the assimilation of solid values, broad spiritual horizons and a deep vision of the cultural environment.\xspace}
\DefineOutcome{ñShort}{Understand that human training contributes to authentic personal growth.\xspace}
\DefineOutcome{FHShort}{Understand that human training contributes to authentic personal growth.\xspace}
\DefineSpecificOutcome{ñ}{1}{ñ1}{.\xspace}

\DefineOutcome{o}{Improve the conditions of society by putting technology at the service of the human being.\xspace}
\DefineOutcome{oShort}{Put technology at the service of the human being.\xspace}
\DefineOutcome{TASDSHShort}{Put technology at the service of the human being.\xspace}
\DefineSpecificOutcome{o}{1}{o1}{Develop software to solve existing problems in our society.\xspace}

\DefineCompetence{C1}{An intellectual understanding and the ability to apply mathematical foundations and computer science theory.}
\DefineCompetence{C2}{Ability to have a critical and creative perspective in identifying and solving problems using computational thinking. }
\DefineCompetence{C3}{An intellectual understanding of, and an appreciation for, the central role of algorithms and data structures.}
\DefineCompetence{C4}{An understanding of computer hardware from a software perspective, for example, use of the processor, memory, disk drives, display, etc.}
\DefineCompetence{C5}{Ability to implement algorithms and data structures in software.}
\DefineCompetence{C6}{Ability to design and implement larger structural units that utilize algorithms and data structures and the interfaces through which these units communicate.}
\DefineCompetence{C7}{Being able to apply the software engineering principles and technologies to ensure that software implementations are robust, reliable, and appropriate for their intended audience.}
\DefineCompetence{C8}{Understanding of what current technologies can and cannot accomplish. }
\DefineCompetence{C9}{Understanding of computing's limitations, including the difference between what computing is inherently incapable of doing vs. what may be accomplished via future science and technology.}
\DefineCompetence{C10}{Understanding of the impact on individuals, organizations, and society of deploying technological solutions and interventions.}
\DefineCompetence{C11}{Understanding of the concept of the lifecycle, including the significance of its phases (planning, development, deployment, and evolution).}
\DefineCompetence{C12}{Understanding the lifecycle implications for the development of all aspects of computer-related systems (including software, hardware, and human computer interface).}
\DefineCompetence{C13}{Understanding the relationship between quality and lifecycle management}
\DefineCompetence{C14}{Understanding of the essential concept of process as it relates to computing especially program execution and system operation.}
\DefineCompetence{C15}{Understanding of the essential concept of process as it relates to professional activity, especially the relationship between product quality and the deployment of appropriate human processes during product development.}
\DefineCompetence{C16}{Ability to identify advanced computing topics and understanding the frontiers of the discipline.}
\DefineCompetence{C17}{Ability to properly express in oral and written media as expected from a university graduate. }
\DefineCompetence{C18}{Ability to participate actively and as a member of a team. .}
\DefineCompetence{C19}{Ability to effectively identify the goals and priorities of their project, stating the action, the time and resources required.}
\DefineCompetence{C20}{Ability to connect theory and skills learned in academia to real-world occurrences explaining their relevance and utility.}
\DefineCompetence{C21}{Understanding the professional, legal, security, political, humanistic, environmental, cultural and ethical issues.
}
\DefineCompetence{C22}{Ability to demonstrate attitudes and priorities that honor, protect, and enhance the profession's ethical stature and standing..}
\DefineCompetence{C23}{Ability to undertake, complete, and present a capstone project.}
\DefineCompetence{C24}{Understanding the need for lifelong learning and improving skills and abilities.}
\DefineCompetence{C25}{Ability to communicate in a second language.}
 
\DefineCompetence{CS1}{Model and design computer-based systems in a way that demonstrates comprehension of the tradeoff involved in design choices.}
\DefineCompetence{CS2}{Identify and analyze criteria and specifications appropriate to specific problems, and plan strategies for their solution.}
\DefineCompetence{CS3}{Analyze the extent to which a computer-based system meets the criteria defined for its current use and future development.}
\DefineCompetence{CS4}{Deploy appropriate theory, practices, and tools for the specification, design, implementation, and maintenance as well as the evaluation of computer-based systems.}
\DefineCompetence{CS5}{Specify, design, and implement computer-based systems.}
\DefineCompetence{CS6}{Evaluate systems in terms of general quality attributes and possible tradeoffs presented within the given problem.}
\DefineCompetence{CS7}{Apply the principles of effective information management, information organization, and information-retrieval skills to information of various kinds, including text, images, sound, and video. This must include managing any security issues.}
\DefineCompetence{CS8}{Apply the principles of human-computer interaction to the evaluation and construction of a wide range of materials including user interfaces, web pages, multimedia systems and mobile systems..}
\DefineCompetence{CS9}{Identify any risks (and this includes any safety or security aspects) that may be involved in the operation of computing equipment within a given context. }
\DefineCompetence{CS10}{Deploy effectively the tools used for the construction and documentation of software, with particular emphasis on understanding the whole process involved in using computers to solve practical problems. This should include tools for software control including version control and configuration management.}
\DefineCompetence{CS11}{Be aware of the existence of publicly available software and understanding the potential of opensource projects.}
\DefineCompetence{CS12}{Operate computing equipment and software systems effectively.}

\DefineCompetence{CE1}{Specify, design, build, test, verify and validate digital systems, including computers,microprocessor-based systems and communications systems.}
\DefineCompetence{CE2}{Develop specific processors, embedded systems, software development, and optimization of such systems.}
\DefineCompetence{CE3}{Analyze and evaluate computer architectures, including parallel and distributed platforms, as well as developing and optimizing software for them.}
\DefineCompetence{CE4}{Design and implement software for communications system.}
\DefineCompetence{CE5}{Analyze, evaluate and select hardware and software platforms suitable for application support and real-time embedded systems.}
\DefineCompetence{CE6}{Understand, implement and manage the security and safety systems.}
\DefineCompetence{CE7}{Analyze, evaluate, select and configure hardware platforms for the development and implementation of software applications and services. .}
\DefineCompetence{CE8}{Design, deploy, administer and manage computer networks.}

\DefineCompetence{IS1}{Identify, understand and document information systems requirements.}
\DefineCompetence{IS2}{Account for human-computer interfaces and intercultural differences, in order to deliver a quality user experience.}
\DefineCompetence{IS3}{Design, implement, integrate and manage IT systems, enterprise, data and application architectures.}
\DefineCompetence{IS4}{Gestionar los proyectos de sistemas de información, incluyendo el análisis de riesgos, estudios financieros, elaboración de presupuestos, la contratación y el desarrollo, y para apreciar los problemas de mantenimiento de los sistemas de información.}
\DefineCompetence{IS5}{Identificar, analizar y comunicar los problemas, opciones y alternativas de solución, incluidos los estudios de viabilidad.}
\DefineCompetence{IS6}{Identify and understand opportunities created by technological innovations.}
\DefineCompetence{IS7}{Appreciate the relationships between business strategy and information systems, architecture and infrastructure.}
\DefineCompetence{IS8}{Understand business processes and the application of IT to them, including change management, control and risk issues.}
\DefineCompetence{IS9}{Understand and implement secure systems, infrastructures and architectures.}
\DefineCompetence{IS10}{Understand performance and scalability issues.}
\DefineCompetence{IS11}{Manage existing information systems including resources, maintenance, procurement and business continuity issues.}


\DefineCompetence{SE1}{Develop, maintain and evaluate software systems and services to meet all user requirements and behave reliably and efficiently, are affordable to develop and maintain and meet quality standards, applying the theories, principles, methods and best practices of Software Engineering.}
\DefineCompetence{SE2}{Assess customer needs and specify the software requirements to meet those needs, reconciling conflicting goals by finding acceptable compromises within the constraints arising from the cost, time, the existence of systems already developed and the organizations themselves.}
\DefineCompetence{SE3}{Solve integration problems in terms of strategies, standards and technologies available.}
\DefineCompetence{SE4}{Work as an individual and as part of a team to develop and deliver quality software artifacts. Understand diverse processes (activities, standards and lifecycle configurations, formality as distinguished from agility) and roles. Perform measurements and analysis (basic) in projects, processes and product dimensions.}
\DefineCompetence{SE5}{Reconcile conflicting project objectives, finding acceptable compromises within limitations of cost, time, knowledge, existing systems, organizations, engineering economics, finance and the fundamentals of risk analysis and management in a software context.}
\DefineCompetence{SE6}{Design appropriate solutions in one or more application domains using software engineering approaches that integrate ethical, social, legal, and economic concerns.}
\DefineCompetence{SE7}{Demonstrate an understanding of, and apply current theories to, models, and techniques that provide a basis for problem identification and analysis, software design, development, construction and implementation, verification and validation, documentation and quantitative analysis of design elements and software architectures.}
\DefineCompetence{SE8}{Demonstrate an understanding of software reuse and adaptation, perform maintenance, integration, migration of software products and components, prepare software elements for potential reuse and create technical interfaces to components and services.}
\DefineCompetence{SE9}{Demonstrate an understanding of systems of software and their environment (business models,regulations).}

\DefineCompetence{IT1}{Design, implement, and evaluate a computer-based system, process, component, or program to meet desired needs within an organizational and societal context.}
\DefineCompetence{IT2}{Identify and analyze user needs and incorporate them in the selection, creation, evaluation and administration of computer-based systems.}
\DefineCompetence{IT3}{Integrate effectively IT based solutions, including the user environment.}
\DefineCompetence{IT4}{Function as a user advocate. Explain and apply appropriate information technologies and employ best practices standards and appropriate methodologies to help an individual or organization achieve its goals and objectives.}
\DefineCompetence{IT5}{Assist in the creation of an effective project plan.}
\DefineCompetence{IT6}{Manage the information technology resources of an individual or organization.}
\DefineCompetence{IT7}{Anticipate the changing direction of information technology and evaluate and communicate the likely utility of new technologies to an individual or organization.}

\newcommand{\Familiarity}{Familiarity}
\DefineCompetenceLevel{1}{\Familiarity}
\newcommand{\Usage}{Usage}
\DefineCompetenceLevel{2}{\Usage}
\newcommand{\Assessment}{Assessment}
\DefineCompetenceLevel{3}{\Assessment}

\newcommand{\LearningOutcomesTxtEsFamiliarity}{El estudiante {\bf entiende} lo que un concepto es o qué significa. Este nivel de dominio {\bf se refiere a un conocimiento básico} de un concepto en lugar de esperar instalación real con su aplicación. Proporciona una respuesta a la pregunta: {\bf ?`Qué sabe usted de esto?}}
\newcommand{\LearningOutcomesTxtEsUsage}{El alumno es capaz de {\bf utilizar o aplicar} un concepto de una manera concreta. El uso de un concepto puede incluir, por ejemplo, apropiadamente usando un concepto especí­fico en un programa, utilizando una técnica de prueba en particular, o la realización de un análisis particular. Proporciona una respuesta a la pregunta: {\bf ?`Qué sabes de cómo hacerlo?}}
\newcommand{\LearningOutcomesTxtEsAssessment}{El alumno es capaz de {\bf considerar un concepto de múltiples puntos de vista} y/o {\bf justificar la selección de un determinado enfoque} para resolver un problema. Este nivel de dominio implica más que el uso de un concepto; se trata de la posibilidad de seleccionar un enfoque adecuado de las alternativas entendidas. Proporciona una respuesta a la pregunta: {\bf ?`Por qué hiciste eso?}}

\newcommand{\LearningOutcomesTxtEnFamiliarity}{The student understands what a concept is or what it means. This level of mastery concerns a basic awareness of a concept as opposed to expecting real facility with its application. It provides an answer to the question: What do you know about this?}
\newcommand{\LearningOutcomesTxtEnUsage}{The student is able to use or apply a concept in a concrete way. Using a concept may include, for example, appropriately using a specific concept in a program, using a particular proof technique, or performing a particular analysis. It provides an answer to the question: What do you know how to do?}
\newcommand{\LearningOutcomesTxtEnAssessment}{The student is able to consider a concept from multiple viewpoints and/or justify the selection of a particular approach to solve a problem. This level of mastery implies more than using a concept; it involves the ability to select an appropriate approach from understood alternatives. It provides an answer to the question: Why would you do that?}


\DefineOutcome{1}{Analyze a complex computing problem and to apply principles of computing and other relevant disciplines to identify solutiones.\xspace}
\DefineOutcome{1Short}{Analyze a complex computing problem and to apply principles of computing and other relevant disciplines.\xspace}
\DefineSpecificOutcome{1}{1}{1.1}{Apply computational thinking effectively to the solution of everyday problems\xspace}
\DefineSpecificOutcome{1}{2}{1.2}{Evaluate different proposals for computational thinking for the same problem.\xspace}
\DefineSpecificOutcome{1}{3}{1.3}{Apply robotics as a means to develop computational thinking.\xspace}
\DefineSpecificOutcome{1}{4}{1.4}{Identify and efficiently apply various algorithmic strategies and data structures for the solution of a problem given certain space and time constraints.\xspace}
\DefineSpecificOutcome{1}{5}{1.5}{Identify and efficiently apply diverse algorithmic strategies and data structures for the solution of a problem in parallel and distributed environments.\xspace}
\DefineSpecificOutcome{1}{6}{1.6}{Implement distributed solutions using MapReduce.\xspace}
\DefineSpecificOutcome{1}{7}{1.7}{Implement distributed solutions using NoSql databases.\xspace}
\DefineSpecificOutcome{1}{8}{1.8}{Apply machine learning techniques to large data sets.\xspace}
\DefineSpecificOutcome{1}{9}{1.9}{Apply machine learning techniques for the processing and analysis of large volumes obtained in real time\xspace}

\DefineSpecificOutcome{1}{10}{1.10}{Implement distributed solutions using network databases.\xspace}
\DefineSpecificOutcome{1}{11}{1.11}{Understand the difference between an NP-difficult problem and one that has a polynomial solution.\xspace}
\DefineSpecificOutcome{1}{12}{1.12}{Given a problem with a polynomial solution, identify whether it can be solved by a voracious strategy, by a dynamic scheduling strategy or by a strategy of divide and conquer taking into account the size of the input.\xspace}
\DefineSpecificOutcome{1}{13}{1.13}{Modeling database through ER, MR, optimization, transaction and information retrieval models\xspace}
\DefineSpecificOutcome{1}{14}{1.14}{Design the appropriate hardware resources for computing.\xspace}
\DefineSpecificOutcome{1}{15}{1.15}{Learn and apply techniques and mechanisms to perform efficient computing on hardware.\xspace}
\DefineSpecificOutcome{1}{16}{1.16}{Understand the implementation of an Operating System to make efficient use of the hardware available in a system.\xspace}
\DefineSpecificOutcome{1}{17}{1.17}{Study and apply various techniques of efficient control of resources to achieve the processing of information.\xspace}
\DefineSpecificOutcome{1}{18}{1.18}{Define requirements in an integrated fine project.\xspace}
\DefineSpecificOutcome{1}{19}{1.19}{Understand the difference between a problem without a solution (undecidable problem) and a problem that does have a solution\xspace}
\DefineSpecificOutcome{1}{20}{1.20}{Identify and solve a problem that is solvable by automata theory and recognize which is the simplest type of automata that solves the problem.\xspace}
\DefineSpecificOutcome{1}{21}{1.21}{Make the budget required to execute a software-based solution.\xspace}
\DefineSpecificOutcome{1}{22}{1.22}{Write programs from a practical specification and produce realistic graphics.\xspace}
\DefineSpecificOutcome{1}{23}{1.23}{Write programs oriented to solve problems in our environment using computer graphics.\xspace}
\DefineSpecificOutcome{1}{24}{1.24}{Analyze the computational power needed to be able to decipher and calculate the value of a key.\xspace}
\DefineSpecificOutcome{1}{25}{1.25}{Analyze and understand the context of a problem to solve it through robotics.\xspace}

\DefineSpecificOutcome{1}{26}{1.26}{Describe the rotation of a rigid body in terms of angular coordinate, angular speed and angular acceleration.\xspace}
\DefineSpecificOutcome{1}{27}{1.27}{Analyze the rotation of a rigid body when the angular acceleration is constant.\xspace}
\DefineSpecificOutcome{1}{28}{1.28}{Relate the rotation of a rigid body to the linear velocity and acceleration of a point on the body.\xspace}
\DefineSpecificOutcome{1}{29}{1.29}{The meaning of the body's moment of inertia around an axis and how it relates to rotational kinetic energy.\xspace}

\DefineOutcome{2}{Design, implement and evaluate a computing-based solution to meet a given set of computing requirements in the context of the program's discipline.\xspace}
\DefineOutcome{2Short}{Design, implement and evaluate a computing-based solution.\xspace}

\DefineOutcome{3}{Communicate effectively in a variety of professional contexts.\xspace}
\DefineOutcome{3Short}{Communicate effectively in a variety of professional contexts.\xspace}
\DefineSpecificOutcome{3}{1}{3.1}{Clearly transmit technical proposals to audiences in other areas.\xspace}
\DefineSpecificOutcome{3}{2}{3.2}{Transmit technical proposals in the area of computing in English.\xspace}
\DefineSpecificOutcome{3}{3}{3.3}{Transmit technical proposals in English to audiences in other areas.\xspace}
\DefineSpecificOutcome{3}{4}{3.4}{Present a business plan to potential investors.\xspace}

\DefineSpecificOutcome{3}{5}{3.5}{Listening. Can follow a very slow and carefully articulated speech to assimilate meaning.\xspace}
\DefineSpecificOutcome{3}{6}{3.6}{Speaking. Can produce simple mainly isolated phrases about people and places.\xspace}
\DefineSpecificOutcome{3}{7}{3.7}{Reading. Can understand very short, simple texts a single phrase at a time, picking up familiar names, words and basic phrases.\xspace}
\DefineSpecificOutcome{3}{8}{3.8}{Writing. Can write simple isolated phrases and sentences.\xspace}

\DefineSpecificOutcome{3}{9}{3.9}{Listening. Can understand a clearly and slowly articulated speech related to areas of most immediate priority.\xspace}
\DefineSpecificOutcome{3}{10}{3.10}{Speaking. Can give a simple description or presentation as a short series of simple phrases and sentences linked into a list.\xspace}
\DefineSpecificOutcome{3}{11}{3.11}{Reading. Can understand short, simple texts containing the highest frequency vocabulary.\xspace}
\DefineSpecificOutcome{3}{12}{3.12}{Writing. Can write a series of simple phrases and sentences linked with simple connectors.\xspace}
\DefineSpecificOutcome{3}{13}{3.13}{Listening. Can understand enough to be able to meet needs of a concrete type.\xspace}
\DefineSpecificOutcome{3}{14}{3.14}{Reading. Can understand short, simple texts on familiar matters of a concrete type which consist of high frequency every day or job-related language.\xspace}

\DefineSpecificOutcome{3}{15}{3.15}{Listening. Can understand the main points of clear standard speech on familiar matters, including short narratives.\xspace}
\DefineSpecificOutcome{3}{16}{3.16}{Speaking. Can reasonably fluently sustain a straightforward description of one of a variety of subjects within his/her field of interest.\xspace}
\DefineSpecificOutcome{3}{17}{3.17}{Reading. Can read straightforward factual texts on subjects related to his/her field and interest with a satisfactory level of comprehension.\xspace}
\DefineSpecificOutcome{3}{18}{3.18}{Writing. Can write straightforward connected texts on a range of familiar subjects by linking a series of shorter discrete elements into a linear sequence.\xspace}
\DefineSpecificOutcome{3}{19}{3.19}{Listening. Can understand straightforward factual information in a generally familiar accent.\xspace}
\DefineSpecificOutcome{3}{20}{3.20}{Speaking. Can reasonably fluently sustain a straightforward description of one of a variety of subjects within his/her field of interest, presenting it as a linear sequence of points.\xspace}

\DefineSpecificOutcome{3}{21}{3.21}{Management of intellectual skills such as memory, concentration, mental agility and creativity.\xspace}
\DefineSpecificOutcome{3}{22}{3.22}{Management of voice, body and facial expression.\xspace}
\DefineSpecificOutcome{3}{23}{3.23}{Strengthen self-esteem, security and overcome shyness (not understood as introversion).\xspace}
\DefineSpecificOutcome{3}{24}{3.24}{Develop clarity, accuracy, linguistic correctness, conciseness and elegance when speaking in a speech.\xspace}
\DefineSpecificOutcome{3}{25}{3.25}{Develop voice qualities such as: volume, speed, tone, flexibility and intonation through breathing exercises.\xspace}
\DefineSpecificOutcome{3}{26}{3.26}{Develop knetic and proxemic skills such as: gestures, use of the hands (mimics and gestures), look, body postures and movements.\xspace}
\DefineSpecificOutcome{3}{27}{3.27}{Structure discourses for different areas such as: scientific, academic and social.\xspace}
\DefineSpecificOutcome{3}{28}{3.28}{Apply team leadership tools such as: effective communication, emotional intelligence, time management, decision making, creativity and innovation, mentoring.\xspace}

\DefineOutcome{4}{Recognize professional responsabilities and make informed judgments in computing practice based on legal and ethical principles.\xspace}
\DefineOutcome{4Short}{Recognize professional responsabilities and make informed judgments.\xspace}

\DefineOutcome{5}{Function effectively as a member or leader of a team engaged in activities appropriate to the program's discipline.\xspace}
\DefineOutcome{5Short}{Function effectively as a member or leader of a team .\xspace}

\DefineOutcome{6}{Apply computer science theory and software development fundamentals to produce computing-based solutions.\xspace}
\DefineOutcome{6Short}{Apply computer science theory and software development fundamentals.\xspace}

\DefineOutcome{7}{Develop principles research in the area of computing with levels of international competitiveness.\xspace}
\DefineOutcome{7Short}{Develop principles of research with international level.\xspace}

\DefineOutcome{8}{Transform your knowledge of the area of Computer Science into technological enterprises.\xspace}
\DefineOutcome{8Short}{Transform your knowledge into technological ventures.\xspace}

\DefineOutcome{9}{Apply knowledge of the humanities in their professional work.\xspace}
\DefineOutcome{9Short}{Apply knowledge of the humanities in their professional work.\xspace}

% \DefineOutcome{10}{Understand that the formation of a good professional is not disconnected or opposed but rather contributes to genuine personal growth. This requires the assimilation of solid values, broad spiritual horizons and a deep vision of the cultural environment.\xspace}
% \DefineOutcome{10Short}{Understand that human training contributes to authentic personal growth.\xspace}

\DefineOutcome{10}{Improve the conditions of society by putting technology at the service of the human being.\xspace}
\DefineOutcome{10Short}{Put technology at the service of the human being.\xspace}

