\begin{syllabus}

<<<<<<< HEAD
\course{CS1703236. Programación Competitiva}{Obligatorio}{CS1703236} % Common.pm
=======
\course{CS311. Programación Competitiva}{Obligatorio}{CS311} % Common.pm
>>>>>>> 1b5a069032d66f0a8c046c7388bce355761e1a06

\begin{justification}
Competitive Programming combines problem-solving challenges with the fun of competing with others. It teaches participants to think faster and develop problem-solving skills that are in high demand in the industry.
This course will teach you to solve algorithmic problems quickly by combining theory of algorithms and data structures with practice solving problems.
\end{justification}

\begin{goals}
\item That the student uses techniques of data structures and complex algorithms..
\item That the student apply the concepts learned for the application on a real problem.
\item That the student investigate the possibility of creating a new algorithm and / or new technique to solve a real problem.
\end{goals}

\begin{outcomes}{V1}
    \item \ShowOutcome{a}{2}
    \item \ShowOutcome{b}{2}
    \item \ShowOutcome{h}{2}
\end{outcomes}

\begin{outcomes}{V2}
    \item \ShowOutcome{1}{2}
    \item \ShowOutcome{2}{2}
    \item \ShowOutcome{4}{2}
    \item \ShowOutcome{5}{2}
\end{outcomes}

\begin{competences}{V1}
    \item \ShowCompetence{C1}{a,b}
    \item \ShowCompetence{C2}{a,b}
    \item \ShowCompetence{C24}{h}
\end{competences}

\begin{competences}{V2}
    \item \ShowCompetence{C1}{1,2}
    \item \ShowCompetence{C2}{1,2}
    \item \ShowCompetence{C24}{4,5}
\end{competences}

\begin{unit}{Primera Unidad}{}{Cormen2009}{20}{C24,C1}
\begin{topics}
        \item Data structure
        \item Dynamic programming
        \item Graph-based algorithms
        \item Sort algorithms
\end{topics}
\begin{learningoutcomes}
        \item Learning to select the right algorithms for a given problem, integrating multiple algorithms for solving a complex problem. [\Usage]
	\item Design new algorithms for real-world problem solving.[\Usage]
\end{learningoutcomes}
\end{unit}

\begin{coursebibliography}
\bibfile{Computing/CS/CS311}
\end{coursebibliography}

\end{syllabus}
