\begin{syllabus}

\course{CS3909. Pre Professional Project}{Obligatorio}{CS3909} % Common.pm

\begin{justification}
This course aims to learn how to make a research of a scientific nature in the area of computing. The course teachers will determine a study area for each student, and will be given bibliography to analyze and from the same, and additional bibliographic sources (investigated by the student), the student should be able to construct an article of the Type survey of the assigned topic.
\end{justification}

\begin{goals}
\item Let the student learn how to start a scientific research in the area of computing.
\item That the student knows the main sources to obtain bibliography relevant for research works in the area of computation: Researchindex, IEEE-CS\footnote{http://www.computer.org}, ACM\footnote{http://www.acm.org}.
\item That the student is able to analyze the existing proposals on a particular topic and relate them consistently in a bibliographic review.
\item That the student can write technical documents in computing using\LaTeX.
\item That the student is able to \underline{reproducir} The results already existing in a given topic through experimentation .
\item Los entregables de este curso son:
	\begin{description}
	\item [Partial Advancement:] Dominio del tema del artículo y bibliografía preliminar en formato de artículo \LaTeX.
	\item [Final:] Understanding of the article of the survey type, document concluded where the experimental results of the studied techniques are optionally contained.
	\end{description}
\end{goals}

\begin{outcomes}{V1}
  \item \ShowOutcome{b}{1}
  \item \ShowOutcome{c}{1}
  \item \ShowOutcome{e}{2}
  \item \ShowOutcome{f}{1}
  \item \ShowOutcome{i}{2}
  \item \ShowOutcome{l}{1}
\end{outcomes}

\begin{outcomes}{V2}
  \item \ShowOutcome{2}{2}
  \item \ShowOutcome{3}{2}
  \item \ShowOutcome{4}{2}
  \item \ShowOutcome{6}{2}
\end{outcomes}

\begin{competences}{V1}
    \item \ShowCompetence{C1}{b,c} 
    \item \ShowCompetence{C20}{e,f.g}
    \item \ShowCompetence{CS2}{i,l}
\end{competences}

\begin{competences}{V2}
    \item \ShowCompetence{C1}{2} 
    \item \ShowCompetence{C20}{3,4}
    \item \ShowCompetence{CS2}{2,6}
\end{competences}

\begin{unit}{}{Pre Professional Job in a Company of the Sector}{ieee,acm,citeseer}{60}{C1,C20,CS2}
  \begin{topics}
      \item Bibliographic search in computer science.
      \item Writing technical articles in computing.
  \end{topics}
  \begin{learningoutcomes}
      \item Learn to do a correct research in the area of computing[\Usage]
      \item To know the sources of adequate bibliography for this area[\Usage]
      \item Know how to write a document according to the characteristics that conferences in this area require[\Usage]
  \end{learningoutcomes}
\end{unit}

\begin{coursebibliography}
\bibfile{Computing/CS/CS401}
\end{coursebibliography}

\end{syllabus}
