\begin{syllabus}

\course{GH0007. Introduction to Business Development}{Obligatorio}{GH0007}
% Source file: ../Curricula.in/lang/English/cycle/2019-II/Syllabi/GeneralEducation/GH1007.tex

\begin{justification}
This course aims to provide students with a real-life hands-on experience in the first steps within a business life cycle, through which an idea becomes a formal business model.
It is the first of a set of three courses designed to accompany students as they transform an idea into a prospective business or business, from idea to review of current business strategy.
\end{justification}

\begin{goals}
   \item Ability to analyze information.
   \item Interpretation of information and results.
   \item Teamwork Ability.
   \item Ethics.
   \item Oral communication.
   \item Written communication.
   \item Graphic communication.
   \item Understand the need to learn continuously
\end{goals}

\begin{outcomes}{V1}
    \item \ShowOutcome{d}{2} % Multidiscip teams
    \item \ShowOutcome{e}{2} % ethical, legal, security and social implications
    \item \ShowOutcome{f}{2} % communicate effectively
    \item \ShowOutcome{n}{2} % Apply knowledge of the humanities
    \item \ShowOutcome{o}{2} % TASDSH
\end{outcomes}

\begin{competences}{V1}
    \item \ShowCompetence{C10}{d,n,o}
    \item \ShowCompetence{C17}{f}
    \item \ShowCompetence{C18}{e}
\end{competences}

\begin{unit}{Introduction to Business Development.}{}{Osterwalder10}{12}{4}
   \begin{topics}
      \item The business lifecycle: from the idea to reviewing your strategy.
      \item The ideation process and the customers view.
      \item How to build and maintain effective teams?
      \item Running LEAN: the basics.
      \item Designing a business model: design tools and Canvas.
      \item Business Model generation: the Canvas Business Model (Osterwalder).
      \item Venture Engineering: using computer science skills to build an effective business model.
      \item Primary market research tools and market niches.
      \item The Importance of Capital: Human, Financial and Intellectual.
      \item Monetizing and Financing Techniques.
      \item Effective communication: making an impact business model presentation.
   \end{topics}
   \begin{learningoutcomes}
      \item Transform an initial business idea or an innovation process into a feasible business model.
   \end{learningoutcomes}
\end{unit}

\begin{coursebibliography}
\bibfile{GeneralEducation/GH1007}
\end{coursebibliography}

\end{syllabus}
