\begin{syllabus}

\course{GH0008. Business Management }{Obligatorio}{GH0008} % Common.pm

\begin{justification}
.
\end{justification}
This course aims to provide students with the tools needed to go a step beyond the initial idea and business model. They will learn the first steps towards conceptualizing a company and building its team. They will also explore the basics of creating an effective business plan. It’s the second of a set of three courses
designed to accompany students as they transform an idea into a business or venture, from ideation to the revision of current business strategy.
\begin{goals}
\item Understanding the basics of the business planning process and its role within the business life cycle.
\end{goals}

\begin{outcomes}{V1}
   \item \ShowOutcome{f}{2}
   \item \ShowOutcome{h}{2}
   \item \ShowOutcome{n}{2}
\end{outcomes}

\begin{competences}{V1}
    \item \ShowCompetence{C17}{f,h,n}
    \item \ShowCompetence{C20}{f,n}
    \item \ShowCompetence{C24}{f,h}
\end{competences}

\begin{unit}{Business Management}{}{Maurya12,Kotler03}{16}{C17,C20}
\begin{topics}
      \item The business lifecycle: why do I need a business plan?
      \item Differences between business model and business planning.
      \item The importance of a well-structured team.
      \item Environmental analysis and main market research tools.
      \item Strategic Planning: Why it is necessary and how it is done.
      \item The importance of capital: human, financial, and intellectual.
      \item How to build an operations plan
      \item The basics of marketing: defining marketing strategy.
      \item Financial Projections : costs and sales.
      \item Legal issues.
      \item Responsible Businesses: the basics.
\end{topics}

\begin{learningoutcomes}
   \item Understood the importance of effective planning and how it contributes to a company has launch and success.
\end{learningoutcomes}
\end{unit}

\begin{coursebibliography}
\bibfile{BusinessAndManagement/BM101}
\end{coursebibliography}

\end{syllabus}
