\begin{syllabus}

\course{CS351. Topics in Computer Graphics}{Electivo}{CS351}
% Source file: ../Curricula.in/lang/English/cycle/2021-I/Syllabi/Computing/CS/CS351.tex

\begin{justification}
In this course you can delve into any of the topics
Mentioned in the area of Graphics Computing (Graphics and Visual Computing - GV).

This course is designed to perform some advanced course suggested by the ACM / IEEE curriculum. \cite{Foley13,Hearn90}
\end{justification}

\begin{goals}
\item That the student uses computer techniques Graphs that involve complex data structures and algorithms.
\item That the student apply the concepts learned to create an application about a real problem.
\item That the student investigate the possibility of creating a new algorithm and / or new technique to solve a real problem
\end{goals}

\begin{outcomes}{V1}
    \item \ShowOutcome{a}{2}
    \item \ShowOutcome{b}{2}
    \item \ShowOutcome{l}{2}
\end{outcomes}

\begin{specificoutcomes}{V1}
    \item \ShowSpecificOutcome{a}{48}{}
    \item \ShowSpecificOutcome{b}{23}{}
    \item \ShowSpecificOutcome{l}{2}{}
\end{specificoutcomes}

\begin{outcomes}{V2}
    \item \ShowOutcome{1}{2}
    \item \ShowOutcome{2}{2}
    \item \ShowOutcome{6}{2}
    \item \ShowOutcome{6}{2}
\end{outcomes}

\begin{competences}{V1}
    \item \ShowCompetence{C1}{a,b}
    \item \ShowCompetence{C20}{l,m}
\end{competences}

\begin{competences}{V2}
    \item \ShowCompetence{C1}{1,2}
    \item \ShowCompetence{C20}{6}
\end{competences}

\begin{unit}{Advanced Topics on Computer Graphics}{}{Soars022S,Soars022W,Soars022T, Cambridge06, MacGrew99}{0}{a,b,m}
   \begin{topics}
      \item CS355. Advanced Computer Graphics
      \item CS356. Computer animation
      \item CS313. Geometric Algorithms
      \item CS357. visualization
      \item CS358. Virtual reality
      \item CS359. Genetic algorithms
   \end{topics}

   \begin{learningoutcomes}
      \item Advanced Topics on Computer Graphics
   \end{learningoutcomes}
\end{unit}

\begin{coursebibliography}
\bibfile{Computing/CS/CS251}
\end{coursebibliography}

\end{syllabus}
