\begin{syllabus}

\course{CS401. Methodology of Computation Research }{Obligatorio}{CS401}
% Source file: ../Curricula.in/lang/English/cycle/2021-I/Syllabi/Computing/CS/CS401.tex

\begin{justification}
  The objective of this course is for the student to learn how to carry out scientific research in the area of computers. The teachers of the course will determine an area of study for each student, and the student will be given a bibliography to analyze. From this bibliography, and from additional bibliographic sources (researched by the student), the student should be able to construct a survey type article on the assigned topic.
\end{justification}

\begin{goals}
\item That the student learns how to start a scientific investigation in the area of computing.
\item That the student knows the main sources to obtain relevant bibliography for research works in the area of computing: Researchindex, IEEE-CS\footnote{http://www.computer.org}, ACM\footnote{http://www.acm.org}.
\item That the student is able to analyze the existing proposals on a certain topic and relate them in a coherent way in a bibliographic review.
\item That the student can write technical documents in computing using \LaTeX.
\item The student will be able to \underline{reproduce} the existing results on a given topic through experimentation.
\item The deliverables of this course are:
	\begin{description}
	\item [Parcial advance:] Mastery of the subject of the article and preliminary bibliography in article format \LaTeX.
	\item [Final:] Understanding of the survey type article, concluded document containing, optionally, the experimental results of the studied technique(s).
	\end{description}
\end{goals}

\begin{outcomes}{V1}
    \item \ShowOutcome{a}{2}
    \item \ShowOutcome{b}{2}
    \item \ShowOutcome{c}{2}
    \item \ShowOutcome{d}{2}
    \item \ShowOutcome{e}{2}
    \item \ShowOutcome{f}{2}
    \item \ShowOutcome{h}{2}
    \item \ShowOutcome{i}{2}
    \item \ShowOutcome{k}{2}
    \item \ShowOutcome{l}{2}
    \item \ShowOutcome{o}{3}
\end{outcomes}

\begin{specificoutcomes}{V1}
    \item \ShowSpecificOutcome{a}{27}{}
    \item \ShowSpecificOutcome{b}{10}{}
    \item \ShowSpecificOutcome{c}{11}{}
    \item \ShowSpecificOutcome{d}{1}{}
    \item \ShowSpecificOutcome{d}{5}{}
    \item \ShowSpecificOutcome{e}{1}{}
    \item \ShowSpecificOutcome{e}{2}{}
    \item \ShowSpecificOutcome{e}{9}{}
    \item \ShowSpecificOutcome{f}{1}{}
    \item \ShowSpecificOutcome{f}{2}{}
    \item \ShowSpecificOutcome{f}{3}{}
    \item \ShowSpecificOutcome{g}{1}{}
    \item \ShowSpecificOutcome{g}{2}{}
    \item \ShowSpecificOutcome{h}{1}{}
    \item \ShowSpecificOutcome{h}{2}{}
    \item \ShowSpecificOutcome{i}{2}{}
    \item \ShowSpecificOutcome{k}{10}{}
    \item \ShowSpecificOutcome{l}{1}{}
    \item \ShowSpecificOutcome{o}{1}{}
\end{specificoutcomes}

\begin{competences}{V1}
    \item \ShowCompetence{C1}{a,b,c} 
    \item \ShowCompetence{C20}{e,f.g}
    \item \ShowCompetence{CS2}{h,i,l}
\end{competences}

\begin{unit}{}{Scientific initiation in the area of computing}{ieee,acm,citeseer}{60}{a,b,c,i,h}
  \begin{topics}
      \item Bibliographic search in computers.
      \item Writing technical articles on computers.
  \end{topics}
  \begin{learningoutcomes}
      \item Learn to do correct research in the area of computing. [\Usage]
      \item Knowing the sources of adequate literature for this area. [\Usage]
      \item Knowing how to write a document in accordance with the characteristics that the conferences in this area require. [\Usage]
  \end{learningoutcomes}
\end{unit}

\begin{coursebibliography}
\bibfile{Computing/CS/CS401}
\end{coursebibliography}

\end{syllabus}
