\begin{syllabus}

\course{GH0010. Ethics and Technology }{Obligatorio}{GH0010}
% Source file: ../Curricula.in/lang/English/cycle/2020-0/Syllabi/GeneralEducation/GH2010.tex

\begin{justification}
This course seeks to provide students with certain frameworks with which to analyze the dilemmas that can be presented in their professional practice. The course puts in practice the critical and responsible reasoning of the students, being this a fundamental competence for the decision-making processes that we will assume as professionals and citizens.
\end{justification}

\begin{goals}
\item Introduce students to critical and ethical thinking applied to their professional field.
\item Developing the competence to look at a phenomenon from various disciplines and perspectives generates in the person empathy and respect for diversity of opinion.
\item Ability to work in a team.
\item Ability to identify problems
\item Oral communication skills
\item He is interested in learning about current issues of Peruvian society and the world.
\item Written communication skills..
\end{goals}

\begin{outcomes}{V1}
    \item \ShowOutcome{d}{2}
    \item \ShowOutcome{e}{2}
    \item \ShowOutcome{f}{2}
    \item \ShowOutcome{n}{2}
    \item \ShowOutcome{o}{2}
\end{outcomes}

\begin{competences}{V1}
    \item \ShowCompetence{C10}{d,n,o}
    \item \ShowCompetence{C17}{f}
    \item \ShowCompetence{C18}{f}
    \item \ShowCompetence{C21}{e}
\end{competences}

\begin{unit}{Etichs, science and technology.}{}{Garcia06}{12}{4}
   \begin{topics}
      \item Definition and scope of ethics Critical thinking / ethical argumentation.
      \item Science and Technology, are engineering and technology issues objective?
      \item Technology: concept and limits.
      \item Importance of ethics in science and engineering.
   \end{topics}
   \begin{learningoutcomes}
      \item Strengthen the student's ability to think interdisciplinarily.
   \end{learningoutcomes}
\end{unit}

\begin{unit}{Responsability of the science and engineering.}{}{Alvarado05}{24}{3}
   \begin{topics}
      \item Scope of the concept Responsibility in science (Imperative of Responsability)
      \item Introduction to the subject Responsibility / freedom
   \end{topics}

   \begin{learningoutcomes}
      \item Understand professional and ethical responsibilities.
   \end{learningoutcomes}
\end{unit}

\begin{unit}{Citizenship and the exercise of justice in the digital era.}{}{Alvarado05}{30}{3}
   \begin{topics}
      \item Introduction to the issue of citizenship in the digital age
      \item Technology, new activism and citizenship
   \end{topics}

   \begin{learningoutcomes}
      \item  Understands the impact of engineering solutions in a global, economic, environmental and societal context.
   \end{learningoutcomes}
\end{unit}

\begin{coursebibliography}
\bibfile{GeneralEducation/GH2010}
\end{coursebibliography}

\end{syllabus}
