\begin{syllabus}

\course{ID301. English V}{Obligatorio}{ID105}

\begin{justification}
A fundamental part of the integral formation of a professional is the ability to communicate in a foreign language in addition to the native language itself.
It not only broadens its cultural horizon but also allows a more humane and comprehensive view of life. In the case of foreign languages, undoubtedly English is the most practical because it is spoken around the world. There is no country where it is not spoken. In careers related to tourist services, English is perhaps the most important practical tool that the student must master from the outset as part of his / her integral education
\end{justification}

\begin{goals}
\item Increase the ability and fluency of speaking and understanding the English language.
\item That the students interact with greater emphasis in the creation of dialogues.
\end{goals}

\begin{competences}
    \item \ShowCompetence{C25}{f,i}
\end{competences}

\begin{outcomes}
\item \ShowOutcome{f}{2}
\item \ShowOutcome{i}{2}
\end{outcomes}

\begin{unit}{It's a wonderful world}{Soars023S,Soars023W,Soars023T, Cambridge06, MacGrew99}{0}{5}
   \begin{topics}
      \item Auxiliary verbs
      \item Verb tenses
      \item Negative Questions and Prayers
      \item Short answers
      \item Word formation
      \item Colloquial expressions
      \item Error correction
   \end{topics}

   \begin{learningoutcomes}
      \item At the end of the first unit, each student, understanding the grammar of auxiliaries and different types of sentences, is able to express a greater number of expressions of time and also use prepositions to describe varied places and times. He is also able to analyze and express ideas about word formation.
   \end{learningoutcomes}
\end{unit}

\begin{unit}{Happiness!}{Soars023S,Soars023W,Soars023T, Cambridge06, MacGrew99}{0}{5}
   \begin{topics}
      \item Simple present
      \item Present continuous
      \item Passive Voice in Present
      \item Verbs for sports and free time
      \item Types of numbers and 
      \item Inventions / Modern World
      \item Corrección de errores
   \end{topics}

   \begin{learningoutcomes}
      \item  At the end of the second unit, students have identified how to express sports and leisure activities. It uses all kinds of numerical expressions. Express situations and states related to present forms. Explain and apply vocabulary of outdoor activities.
   \end{learningoutcomes}
\end{unit}

\begin{unit}{Telling tales!}{Soars023S,Soars023W,Soars023T, Cambridge06, MacGrew99}{0}{5}
   \begin{topics}
      \item Simple Past Time
      \item Past Continuous
      \item Passive Voice in Past
      \item Vocabulary of Art and Literature
      \item Expressions to give and ask opinions
      \item Stories and stories
   \end{topics}

   \begin{learningoutcomes}
      \item At the end of the third unit, students having recognized the characteristics of the past passive forms, they use these make descriptions of various types. Describe art and literature and give indications of opinion. They will use conjunctions to unite type ideas.
   \end{learningoutcomes}
\end{unit}

\begin{unit}{Doing the right thing!}{Soars023S,Soars023W,Soars023T, Cambridge06, MacGrew99}{0}{5}
   \begin{topics}
      \item Mode Auxiliary Verbs I.
      \item Affirmative, Negative and Modals Questions
      \item Use of nationalities and other adjectives
      \item Expressions of orders and offers
      \item Guide to Good Manners
      \item Form Fill
      \item Phonetic symbols
   \end{topics}

   \begin{learningoutcomes}
      \item At the conclusion of the fourth unit, the students having identified the idea of expressing ideas of modes of actions that happen at the moment or that are related at any time, structure sentences in the Present. They express ideas of nationalities and make requests and offers varied.
   \end{learningoutcomes}

\end{unit}

\begin{unit}{On the move!}{Soars023S,Soars023W,Soars023T, Cambridge06, MacGrew99}{0}{5}
   \begin{topics}
      \item Future with Will
      \item Future Time Prayers with going to
      \item Use of might for future
      \item Climate Expressions
      \item Vocabulary of the climate
      \item Expressions for hotels and transportation
      \item E-mails
   \end{topics}

   \begin{learningoutcomes}
      \item At the end of the fifth unit, students, from the understanding of future time, will elaborate sentences using the necessary elements. They will also assimilate the need to express ideas of the climate. They will acquire vocabulary to describe use of public transportation. Expressions will be presented to order at hotels.
   \end{learningoutcomes}

\end{unit}

\begin{unit}{I just love it!}{Soars023S,Soars023W,Soars023T, Cambridge06, MacGrew99}{0}{5}
   \begin{topics}
      \item Questions with Shapes Like
      \item Patrones Verbales II
      \item Vocabulario de Comida, Lugares y ocupaciones
      \item Palabras que van unidas en contexto
      \item Expresiones para vistas y sonidos
      \item Composición de Impresiones personales
   \end{topics}

   \begin{learningoutcomes}
      \item At the end of the sixth unit, students having learned the basics of structuring questions with like and with verbal patterns work applied to appropriate contexts. They emphasize the difference between meals, places and people. Describe sights and sounds. They use expressions to compare daily life in different places. They assume the idea of different lifestyles.
   \end{learningoutcomes}
\end{unit}

\begin{coursebibliography}
\bibfile{ForeignLanguages/ID101}
\end{coursebibliography}

\end{syllabus}
