\begin{syllabus}

\course{CB101. Álgebra y Geometría}{Obligatorio}{CB101}

\begin{justification}
This course is designed to provide students with a sound understanding of the innovation process within a company. It focuses on applying entrepreneurial innovation skills within a well-established company. This is known as Intrapreneurship.
It’s the third of a set of three courses designed to accompany students as they transform an idea into a prospective business or venture. The student will experience the process from the phase of ideation to reviewing current business strategies. 
The material seen in this course answers 2 main questions: “What should you do?” and “How should you get it done?”. The objective of this course is that the student will learn how to approach innovation and product development from both the strategic and the implementation processes. 

\end{justification}

\begin{goals}
\item Identify how innovation relates to the entrepreneurial and intrapreneurial process.
\item Familiarize themselves with innovation tools and practice how to make use of them.
\item Learn how to integrate innovation into the business cycle.
\item Understand the importance of strategy and implementation and how an idea needs to be accompanied by an effective implementation plan.
\item Information analysis.
\item Interpreting information and results.
\item Teamwork.
\item Ethics.
\item Oral communication.
\item Written communication.
\item Graphical communication.
\item Understanding the need to learn continuously.
 
\end{goals}

\begin{outcomes}
\ExpandOutcome{a}{3}
\ExpandOutcome{i}{2}
\ExpandOutcome{j}{4}
\end{outcomes}

\begin{unit}{Sistemas de coordenadas. La recta.}{Lehmann05}{12}{4}
   \begin{topics}
      \item 
      \item 
   \end{topics}
   \begin{unitgoals}
      \item 
   \end{unitgoals}
\end{unit}

\begin{unit}{Cónicas y Coordenadas polares}{Lehmann05}{24}{3}
   \begin{topics}
      \item 
      \item 
   \end{topics}

   \begin{unitgoals}
      \item 
      \item
      \item 
      \end{unitgoals}
\end{unit}

\begin{unit}{Sistemas de ecuaciones. Matrices y determinantes}{Strang03,Grossman96}{24}{3}
   \begin{topics}
      \item 
      \item 
      \item 
      \end{topics}

   \begin{unitgoals}
      \item 
      \item 
      \item 
     
   \end{unitgoals}
\end{unit}

\begin{unit}{Vectores en $R^2$ y vectores en $R^3$}{Grossman96}{30}{3}
   \begin{topics}
      \item 
      \item 
   \end{topics}

   \begin{unitgoals}
      \item 
      \item 
      \item 
   \end{unitgoals}
\end{unit}



\begin{coursebibliography}
\bibfile{GeneralH/GH0011}
\end{coursebibliography}

\end{syllabus}
