\begin{syllabus}

\course{CB101. Álgebra y Geometría}{Obligatorio}{CB101}

\begin{justification}
The course seeks to give a global, historical and critical vision of the transformations and synergies of contemporary art. Where students approach two components of contemporary art and design: interdisciplinary practices and points of contact between the arts and the technological and engineering processes.
\end{justification}

\begin{goals}
    \item Develop the ability to analyze information.
    \item Develop the ability to interpret information.
    \item Develop the ability to work as a team.
    \item Developing Oral communication skills.
    \item To promote interest in learning about current issues of Peruvian society and the world.
    \item Recognize the need for lifelong learning.
    
\item 
\end{goals}

\begin{outcomes}
\ExpandOutcome{a}{2}
\ExpandOutcome{d}{2}
\ExpandOutcome{f}{3}
\ExpandOutcome{h}{3}
\ExpandOutcome{o}{2}

\end{outcomes}

\begin{unit}{Introducción al curso. ¿Por qué son importantes el arte y el diseño en la ingeniería? .}{Wilson02}{12}{4}
   \begin{topics}
      \item . 
   \end{topics}
   \begin{unitgoals}
      \item 
   \end{unitgoals}
\end{unit}

\begin{unit}{E.A.T. — The Story of Experiments in Art and Technology}{Maeda12}{24}{3}
   \begin{topics}
      \item . 
   \end{topics}

   \begin{unitgoals}
      \item .
      \end{unitgoals}
\end{unit}

\begin{unit}{¿Qué es el arte y para qué sirve?}{Wilson02}{24}{3}
   \begin{topics}
      \item . 
      \end{topics}

   \begin{unitgoals}
      \item .
     
   \end{unitgoals}
\end{unit}

\begin{unit}{Denuncia y Comunicación: El arte como herramienta}{Wilson02}{30}{3}
   \begin{topics}
      \item .
   \end{topics}

   \begin{unitgoals}
      \item .
   \end{unitgoals}
\end{unit}

\begin{unit}{Usos de la tecnología en el arte}{Manda15}{30}{3}
   \begin{topics}
      \item .
   \end{topics}

   \begin{unitgoals}
      \item .
   \end{unitgoals}
\end{unit}
\begin{unit}{Nuevas Fronteras: Real/Virtual}{Maeda12}{30}{3}
   \begin{topics}
      \item .
   \end{topics}

   \begin{unitgoals}
      \item .
   \end{unitgoals}
\end{unit}

\begin{unit}{Processing}{Wilson02}{30}{3}
   \begin{topics}
      \item . 
   \end{topics}

   \begin{unitgoals}
      \item .
   \end{unitgoals}
\end{unit}

\begin{unit}{¿Qué es la identidad? }{Manda15}{30}{3}
   \begin{topics}
      \item . 
   \end{topics}

   \begin{unitgoals}
      \item . 
   \end{unitgoals}
\end{unit}

\begin{unit}{El Error como Oportunidad: Glitch}{Maeda12}{30}{3}
   \begin{topics}
      \item .
   \end{topics}

   \begin{unitgoals}
      \item . 
   \end{unitgoals}
\end{unit}

\begin{unit}{Arte Generativo}{Manda15}{30}{3}
   \begin{topics}
      \item . 
   \end{topics}

   \begin{unitgoals}
      \item . 
   \end{unitgoals}
\end{unit}

\begin{unit}{Net Art}{Wilson02}{30}{3}
   \begin{topics}
      \item .
   \end{topics}

   \begin{unitgoals}
      \item . 
   \end{unitgoals}
\end{unit}

\begin{unit}{Hombre-Maquina: Cyborgs del mundo real}{Manda15}{30}{3}
   \begin{topics}
      \item . 
   \end{topics}

   \begin{unitgoals}
      \item . 
   \end{unitgoals}
\end{unit}

\begin{unit}{Territorio: Problemáticas de la Ciudad}{Wilson02}{30}{3}
   \begin{topics}
      \item .
   \end{topics}

   \begin{unitgoals}
      \item .
   \end{unitgoals}
\end{unit}

\begin{unit}{Espacios Públicos: Del escenario a la calle}{Maeda12}{30}{3}
   \begin{topics}
      \item . 
   \end{topics}

   \begin{unitgoals}
      \item .
   \end{unitgoals}
\end{unit}


\begin{coursebibliography}
\bibfile{GeneralEducation/GH1002}
\end{coursebibliography}
\end{syllabus}
