\begin{syllabus}

\course{GH0011. Innovación y Desarrollo de Productos}{Obligatorio}{GH0011} % Common.pm

\begin{justification}
This course is designed to provide students with a sound understanding of the innovation process within a company. It focuses on applying entrepreneurial innovation skills within a well-established company. This is known as Intrapreneurship.
It's the third of a set of three courses designed to accompany students as they transform an idea into a prospective business or venture. The student will experience the process from the phase of ideation to reviewing current business strategies. 
The material seen in this course answers 2 main questions: What should you do? and How should you get it done?. 
\end{justification}

\begin{goals}
\item Identify how innovation relates to the entrepreneurial and intrapreneurial process.
\item Familiarize themselves with innovation tools and practice how to make use of them.
\item Learn how to integrate innovation into the business cycle.
\item Understand the importance of strategy and implementation and how an idea needs to be accompanied by an effective implementation plan.
\item Information analysis.
\item Interpreting information and results.
\item Teamwork.
\item Ethics.
\item Oral communication.
\item Written communication.
\item Graphical communication.
\item Understands the need to learn on a continuous basis.

\end{goals}

\begin{outcomes}{V1}
    \item \ShowOutcome{d}{2} % Multidiscip teams
    \item \ShowOutcome{e}{2} % ethical, legal, security and social implications
    \item \ShowOutcome{f}{2} % communicate effectively
    \item \ShowOutcome{n}{2} % Apply knowledge of the humanities
    \item \ShowOutcome{o}{2} % TASDSH
\end{outcomes}

\begin{competences}{V1}
    \item \ShowCompetence{C10}{d,n,o}
    \item \ShowCompetence{C17}{f}
    \item \ShowCompetence{C18}{f}
    \item \ShowCompetence{C21}{e}
\end{competences}

\begin{unit}{Innovation and Product development.}{}{Morales13}{12}{4}
   \begin{topics}
      \item Creativity:understanding hor our brain works.
      \item Innovation :Who,what ,why,whe, where?
      \item The big myths on innovation.
      \item Innovation strategies :how to introduce innovation within a company .
      \item The innovation process.
      \item Managing innovation.
      \item How to structure and coordinate innovation.
      \item Implementing and managing innovation.
      \item Corporate spinouts.
      \item Entrepreneurs and intrapreneurs.
      \item Circular economy
      \item Carbon footprint
      \item Eco efficiency.
      \item Product development 
      
   \end{topics}
   \begin{learningoutcomes}
      \item Studens will have  acquired a set of tools to help them along the innovation process ,including innovation management strategies.
   \end{learningoutcomes}
\end{unit}

\begin{coursebibliography}
\bibfile{GeneralEducation/GH2011}
\end{coursebibliography}

\end{syllabus}
